|

### 2019-11-04 analysis/paper/paper.Rmd
Add DOCX export

---
title: |
  Structure and parameter uncertainty in centennial-scale projections
  of community succession in an Upper Midwest temperate forest
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Jeff Atkins
  - Christopher M. Gough
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
    bookdown::pdf_document2:
      latex_engine: xelatex
bibliography: references.bib
csl: "../templates/ecology.csl"
abstract: |
  Forests in the US Upper Midwest have been a net C sink for a century, driven by their fast-growing, early successional species. 
  However, the composition of these regrown forests has started to shift toward mid-successional species. 
  Combined with changing climate and disturbance, this means that future biogeochemical and ecological dynamics in these forests are highly uncertain. 
  Demographic vegetation models provide a tool for analyzing this uncertainty and its implications. 
  Here, we evaluate the relative importance of model "structural" (which processes are represented, and how) and "parameter" (parameters used in those equations) uncertainty, asking: 
  (1) Which processes are most important to accurately model community succession and C cycling in Upper Midwest forests?
  (2) What are the relative contributions of parameter vs. structural uncertainty?
  We ran ensembles of the Ecosystem Demography model v2.2 (sampling over parameter uncertainty) from 1900 to 2000 with different representations of key processes important to competition for light.
  We then compared the magnitude of structural (across representations) and parameter (within each representation) uncertainty, and assessed which submodel-parameter combinations reproduced observed C fluxes and succession.
  On average, our simulations underestimated both net primary productivity (NPP) and leaf area index (LAI) after 100 simulation years, though NPP estimates at peak productivity (20-50 years into the simulations) were closer to observations.
  However, parameter uncertainty was large; at any given timestep, both NPP and LAI ranged from ~0 to >200% of their mean value.
  Although many simulations matched either the observed NPP or observed LAI at some point during the simulation, only a small minority of individual runs matched both.
  The few runs that matched observed NPP and LAI also matched the present-day PFT mixture (early hardwood-dominated) at UMBS.
  Structural uncertainty was less important than parameter uncertainty, but model configuration did influence the ecological dynamics within a given parameter set, and affected which parameters were most influential.
  We conclude that: (1) targeted data collection to constrain vegetation model parameters should be a higher priority than model development; (2) parameter sensitivity analyses are not necessarily generalizable across model structures; and (3) robust model validation requires scrutiny of multiple different variables, including those related to vegetation productivity, structure, and composition.
keywords: |
  Dynamic vegetation modeling; carbon cycle; forest succession
highlights: |
  TODO
---

@@

```{r param-table}
tbl <- readr::read_csv(here(
  "analysis", "data", "derived-data", "parameter-table.csv"
))
tbl <- subset(tbl, Ran == "yes", select = c(-unit_parsed, -Ran))
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
kable(tbl, escape = is_latex_output(), caption = paste0(
  "Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
), booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

>>>>

---
title: |
  Structure and parameter uncertainty in centennial-scale projections
  of community succession in an Upper Midwest temperate forest
author:
  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Jeff Atkins
  - Christopher M. Gough
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
    bookdown::pdf_document2:
      latex_engine: xelatex
    bookdown::word_document2:
      reference_docx: "../templates/taylor-francis-article.docx" # Insert path for the DOCX file
always_allow_html: true
bibliography: references.bib
csl: "../templates/ecology.csl"
abstract: |
  Forests in the US Upper Midwest have been a net C sink for a century, driven by their fast-growing, early successional species.
  However, the composition of these regrown forests has started to shift toward mid-successional species.
  Combined with changing climate and disturbance, this means that future biogeochemical and ecological dynamics in these forests are highly uncertain.
  Demographic vegetation models provide a tool for analyzing this uncertainty and its implications.
  Here, we evaluate the relative importance of model "structural" (which processes are represented, and how) and "parameter" (parameters used in those equations) uncertainty, asking:
  (1) Which processes are most important to accurately model community succession and C cycling in Upper Midwest forests?
  (2) What are the relative contributions of parameter vs. structural uncertainty?
  We ran ensembles of the Ecosystem Demography model v2.2 (sampling over parameter uncertainty) from 1900 to 2000 with different representations of key processes important to competition for light.
  We then compared the magnitude of structural (across representations) and parameter (within each representation) uncertainty, and assessed which submodel-parameter combinations reproduced observed C fluxes and succession.
  On average, our simulations underestimated both net primary productivity (NPP) and leaf area index (LAI) after 100 simulation years, though NPP estimates at peak productivity (20-50 years into the simulations) were closer to observations.
  However, parameter uncertainty was large; at any given timestep, both NPP and LAI ranged from ~0 to >200% of their mean value.
  Although many simulations matched either the observed NPP or observed LAI at some point during the simulation, only a small minority of individual runs matched both.
  The few runs that matched observed NPP and LAI also matched the present-day PFT mixture (early hardwood-dominated) at UMBS.
  Structural uncertainty was less important than parameter uncertainty, but model configuration did influence the ecological dynamics within a given parameter set, and affected which parameters were most influential.
  We conclude that: (1) targeted data collection to constrain vegetation model parameters should be a higher priority than model development; (2) parameter sensitivity analyses are not necessarily generalizable across model structures; and (3) robust model validation requires scrutiny of multiple different variables, including those related to vegetation productivity, structure, and composition.
keywords: |
  Dynamic vegetation modeling; carbon cycle; forest succession
highlights: |
  TODO
---

@@

```{r param-table}
tbl <- readr::read_csv(here(
  "analysis", "data", "derived-data", "parameter-table.csv"
))
tbl <- subset(tbl, Ran == "yes", select = c(-unit_parsed, -Ran))
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
cap <- paste(
  "Parameter descriptions.",
  "For additional information, see the",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
)
if (is_latex_output() || is_html_output()) {
  kable(tbl, escape = is_latex_output(), caption = cap, booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down")
} else {
  # Probably DOCX output
  cap <- paste("Table: (\\#tab:param-table)", cap)
  flextable::flextable(tbl) %>%
    flextable::autofit() %>%
    flextable::fit_to_width(7.5) %>%
    flextable::set_caption(cap)
}
```
